---
title: "Data Visualization For All Mediums"
author: "Keaton Markey"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Another Blog POst About Data Visualization
### Presenting Data in Apps vs Markdown

You've just finished crunching numbers on your most recent data science project, and its time to present your findings to the world. But, there's a couple of issues.

You don't want people to see too many words. Your code might be too long (or messy), or you'd rather have images and figures tell the story.

Maybe your analysis isn't exactly linear (which is often the case), and you want users to be able to jump around easily

You don't want to mess with JavaScript or a more popular app-development library


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
